WrapITK: Enhanced languages support\\ for the Insight Toolkit

### 2006-03-23 article/Article.tex
typo, and complete Benoit s affiliation
darcs-hash:20060323161337-2fc9d-954e146a5562f1d439051e7e7dd1292dc5048b88.gz

% At minimum, give your name and an email address.  You can include a
% snail-mail address if you like.
\author{Ga\"etan Lehmann{$^1$}{\small{,}} Zachary Pincus{$^2$} {\small{and}} Benoit Regrain{$^3$}}
\authoraddress{{$^1$}Unit\'e de Biologie du D\'eveloppement et de la Reproduction, Institut National de la Recherche Agronomique, 78350 Jouy-en-Josas, France\\
{$^2$}Stanford University, CA 94305, USA\\
{$^3$}Creatis, CNRS, 69621 Villeurbanne, France}

@@

  \item Finally, \verb$WRAPPER_LIBRARY_CREATE_LIBRARY()$ creates rules to parse the CalbeSwig
inputs and compile a wrapper library. This macro also causes various language
support files to be created (python only currently) which make it easy to load
that library in python, and which know about the template instances defined.
This macro is defined in \verb$CreateWrapperLibrary.cmake$, and calls language support
macros from \verb$CreateLanguageSupport.cmake$.
\end{itemize}

>>>>

% At minimum, give your name and an email address.  You can include a
% snail-mail address if you like.
\author{Ga\"etan Lehmann{$^1$}{\small{,}} Zachary Pincus{$^2$} {\small{and}} Benoit Regrain{$^3$}}
\authoraddress{{$^1$}Unit\'e de Biologie du D\'eveloppement et de la Reproduction, Institut National de la Recherche Agronomique, 78350 Jouy-en-Josas, France\\
{$^2$}Stanford University, CA 94305, USA\\
{$^3$}CREATIS, CNRS UMR 5515, 69621 Villeurbanne, France}

@@

  \item Finally, \verb$WRAPPER_LIBRARY_CREATE_LIBRARY()$ creates rules to parse the CableSwig
inputs and compile a wrapper library. This macro also causes various language
support files to be created (python only currently) which make it easy to load
that library in python, and which know about the template instances defined.
This macro is defined in \verb$CreateWrapperLibrary.cmake$, and calls language support
macros from \verb$CreateLanguageSupport.cmake$.
\end{itemize}
